Share Buyback and Equity Issue Anomalies Revisited: Interactive Tool

### 2016-03-03 index.Rmd
update

#library(googleVis)
#library("shiny")
#library("reshape2")  
#library("ggplot2")
# Why are these not found when deployed?!
library("shiny") 
library("shinysky") #  devtools::install_github("AnalytixWare/ShinySky")

library("stringr")
library("RcppArmadillo")
library("gtools")
library("timeDate")
source("lib/lib_helpers_shiny.R")
source("lib/Paper_global_parameters.R")
source("lib/heatmapOutput.R") 
source("lib/plots.R")
source("report_helpers.R")

@@

This is an interactive tool for the article [Share Buyback and Equity Issue Anomalies Revisited](http://tevgeniou.github.io/BuybacksIssuers/). Users can explore the effects of various parameters as well as data filtering choices. For any given choices, users can generate and download a new **customized pdf version of the paper** by clicking the button below at any time.

@@

```{r, fig.width=6, fig.height=5,echo=FALSE}
downloadHandler(
  filename = "report.pdf",
  content = function(file) {
    knitr::knit2pdf("report.Rnw",envir=environment())
    file.rename(normalizePath('report.pdf'), file)
  }
)
```

@@

```{r, eval=TRUE, echo = FALSE}
acceptaple_features = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares","Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","Idiosyncraticness","Industry", "Purpose.Code","Source.of.funds")

fluidPage(
  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[1]),
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Histogram",
                         busyIndicator("Please wait while we load the data for you... This shouldn't take more than a few seconds...",wait = 0),
                         renderPlot({
                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Summary Statistics",
                         renderDataTable({
                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                           #feature = feature[!is.na(feature)]
                           if (length(unique(feature)) > 20 & is.numeric(feature)){
                             res = t(as.matrix(summary(feature)))
                             colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
                           }
                           if (is.character(feature) | length(unique(feature)) <= 20){
                             tmp = sort(table(feature), decreasing = TRUE)
                             res = t(as.matrix(tmp))
                           }
                           as.data.frame(res)
                           #m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
                           #print(m1,'chart')
                         })
                )
    ),
    style='width: 100%;'))
```

@@

```{r, eval=TRUE, echo = FALSE}
checkboxGroupInput("industry", "Select Industries  to remove:", choices = unique(DATASET_INI$SDC$Industry),selected = "Software",inline=TRUE)

@@

feature_IRATStable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  res = round(cbind(
    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  res = round(cbind(
    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly,report_months_cal)$results,
    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly,report_months_cal)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

@@

```{r, eval=TRUE, echo = FALSE}
acceptaple_features1 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","Idiosyncraticness")

selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features1,selected = acceptaple_features1[1], width = "1000px")

@@

  thefeature = as.numeric(scrub(thefeature))
  quantile_used_ind = as.numeric(input$quantile_used_ind)

@@

```{r, eval=TRUE, echo = FALSE}
acceptaple_features2 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","Idiosyncraticness","None")
```

<br>
```{r, eval=TRUE, echo = FALSE}
fluidPage( 
  h4("Firm Characteristics of the new index"),
  fluidRow(
    column(6,
      selectInput("characteristic_irats1", "First Firm Characteristic:", choices = acceptaple_features2,selected = acceptaple_features2[1], width = "425px"),
      checkboxInput("characteristic_irats1_sign", "Reverse", value = FALSE),
      selectInput("characteristic_irats2", "Second Firm Characteristic:", choices = acceptaple_features2,selected ="None", width = "425px"),
checkboxInput("characteristic_irats2_sign", "Reverse", value = FALSE),
    selectInput("characteristic_irats3", "Third Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
checkboxInput("characteristic_irats3_sign", "Reverse", value = FALSE)
     ),
  column(6,
      selectInput("characteristic_irats4", "Fourth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
      checkboxInput("characteristic_irats4_sign", "Reverse", value = FALSE),
    selectInput("characteristic_irats5", "Fifth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
    checkboxInput("characteristic_irats5_sign", "Reverse", value = FALSE),
    selectInput("characteristic_irats6", "Sixth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
    checkboxInput("characteristic_irats6_sign", "Reverse", value = FALSE)
    )
  )
)
```

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_IRATStable_index()
                         })),
                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_CALtable_index()
                         })),
                tabPanel("Histogram of the New Index",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderPlot({
                           feature = Index_Score_rect()
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Cumulative Abnormal Returns,High, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderDygraph({
                           pnl_plot_interactive(High_feature_Hedged_react_index())
                         })),
                tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderDygraph({
                           pnl_plot_interactive(Low_feature_Hedged_react_index())
                         })),
                tabPanel("Monthly and Yearly Returns, High, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderUI({
                           renderHeatmapX(pnl_matrix(High_feature_Hedged_react_index()))
                         })),
                tabPanel("Monthly and Yearly Returns, Low, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderUI({
                           renderHeatmapX(pnl_matrix(Low_feature_Hedged_react_index()))
                         }))
    ),style='width: 100%;'))
```

>>>>

if(T) {
  library(googleVis)
  library("shiny")
  library("reshape2")  
  library("ggplot2")
  # Why are these not found when deployed?!
  library("shiny") 
  library("shinysky") #  devtools::install_github("AnalytixWare/ShinySky")

  library("stringr")
  library("RcppArmadillo")
  library("gtools")
  library("timeDate")
  library("dygraphs")
  library("reshape")
  library("ggplot2")
}
source("lib/lib_helpers_shiny.R")
source("lib/Paper_global_parameters.R")
source("lib/heatmapOutput.R") 
source("lib/plots.R")
source("report_helpers.R")

@@

This is an interactive tool for the article [Share Buyback and Equity Issue Anomalies Revisited](http://tevgeniou.github.io/BuybacksIssuers/). Users can explore the effects of various parameters as well as data filtering choices. For any given choices, users can generate and download a new **customized pdf version of the paper** by clicking the buttons which will appear below at any time.

@@

```{r, fig.width=6, fig.height=5,echo=FALSE}
shinyApp(
  ui = fluidPage(
    fluidRow(
      column(2,
        conditionalPanel(
          condition = "!$('makeReport').hasClass('shiny-busy')",
          actionButton("makeReport","Generate Report",icon=icon("file"))
        )
      ),
      column(4,
      conditionalPanel(
        condition = "!$('makeReport').hasClass('shiny-busy')",
        uiOutput("downloadButton")
        #downloadButton("downloadReport", "Download Report")
      )
      )
    ),
    busyIndicator("Please wait while we prepare the report ...",wait = 0)
  ),
  server = function(input, output) {
    output$download_button <- renderUI({
        downloadButton("downloadReport", "Download Results")
     })
    makeReportAction <- eventReactive(input$makeReport, {
      #Create the pdf here
      #Sys.sleep(1);return()
      #first check if we didn't already create a paper with these parameters, if so, load from cache
      #filename <- paste("reports/")
      #file.exists()
      tosave= list("startdate","enddate","market_cap_min","market_cap_max","quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
        newinput <- list()
        for(i in tosave) {
          newinput[[i]] <- input[[i]]
        }
        #save("newinput",file=normalizePath("input.Rdata"))
        knitr::knit2pdf("report.Rnw",envir=globalenv())
    })
    output$downloadButton <- renderUI({
      makeReportAction() #only appear after first click on generate
      downloadButton("downloadReport", "Download Report")
    })
    output$downloadReport <- downloadHandler(
      filename = "report.pdf",
      content = function(file) {
        cat(paste("Does the pdf exist?",file.exists("report.pdf")))
        file.rename(normalizePath('report.pdf'), file)
      }
    )
  },
  options = list(height = 120,width=800)
)

@@

```{r, eval=TRUE, echo = FALSE}
acceptaple_features = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares","Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","Industry", "Purpose.Code","Source.of.funds")

fluidPage(
  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[4]),
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Histogram",
                         busyIndicator("Please wait while we load the data for you... This shouldn't take more than a few seconds...",wait = 0),
                         renderPlot({
                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Summary Statistics",
                         renderDataTable({
                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                           #feature = feature[!is.na(feature)]
                           if (length(unique(feature)) > 20 & is.numeric(feature)){
                             res = t(as.matrix(summary(feature)))
                             colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
                           }
                           if (is.character(feature) | length(unique(feature)) <= 20){
                             tmp = sort(table(feature), decreasing = TRUE)
                             res = t(as.matrix(tmp))
                           }
                           as.data.frame(res)
                           #m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
                           #print(m1,'chart')
                         })
                )
    ),
    style='width: 100%;'))
```

@@

```{r, eval=TRUE, echo = FALSE}
checkboxGroupInput("industry", "Select Industries to remove:", choices = unique(DATASET_INI$SDC$Industry),selected = NULL,inline=TRUE)

@@

feature_IRATStable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  #cat(paste("Total left after filtering industry:",sum(useonly_industry)))
  #instead of using company_subset_undervalued and _overvalued, use Valuation Index
  thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == "Valuation.Index")]]
  thefeature = as.numeric(scrub(thefeature))
  quantile_used_ind = as.numeric(0.2)
  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)

  res = round(cbind(
    #car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
    #car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & Low_feature_events)$results,
    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & High_feature_events)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable_industry <- reactive({
    thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == "Valuation.Index")]]
  thefeature = as.numeric(scrub(thefeature))
  quantile_used_ind = as.numeric(0.2)
  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)

  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  res = round(cbind(
    #calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly,report_months_cal)$results,
    #calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly,report_months_cal)$results
    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & Low_feature_events], DATASET_NEW()$SDC$Event.Date[useonly_industry& Low_feature_events], Risk_Factors_Monthly,report_months_cal)$results,
        calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & High_feature_events], DATASET_NEW()$SDC$Event.Date[useonly_industry & High_feature_events], Risk_Factors_Monthly,report_months_cal)$results

  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

@@

```{r, eval=TRUE, echo = FALSE}
acceptaple_features1 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio")

selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features1,selected = acceptaple_features1[4], width = "1000px")

@@

  thefeature = as.numeric(scrub(thefeature))
  quantile_used_ind = as.numeric(input$quantile_used)

@@

```{r, eval=TRUE, echo = FALSE}
acceptaple_features2 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","None")
```

<br>
```{r, eval=TRUE, echo = FALSE}
fluidPage( 
  h4("Firm Characteristics of the new index"),
  fluidRow(
    column(6,
      selectInput("characteristic_irats1", "First Firm Characteristic:", choices = acceptaple_features2,selected = acceptaple_features2[4], width = "425px"),
      checkboxInput("characteristic_irats1_sign", "Reverse", value = FALSE),
      selectInput("characteristic_irats2", "Second Firm Characteristic:", choices = acceptaple_features2,selected ="None", width = "425px"),
checkboxInput("characteristic_irats2_sign", "Reverse", value = FALSE),
    selectInput("characteristic_irats3", "Third Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
checkboxInput("characteristic_irats3_sign", "Reverse", value = FALSE)
     ),
  column(6,
      selectInput("characteristic_irats4", "Fourth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
      checkboxInput("characteristic_irats4_sign", "Reverse", value = FALSE),
    selectInput("characteristic_irats5", "Fifth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
    checkboxInput("characteristic_irats5_sign", "Reverse", value = FALSE),
    selectInput("characteristic_irats6", "Sixth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
    checkboxInput("characteristic_irats6_sign", "Reverse", value = FALSE)
    )
  )
)
```

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Histogram of the New Index",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderPlot({
                           feature = Index_Score_rect()
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 20,main="Index Histogram",xlab="Score")
                         })),
                tabPanel("Five-Factor IRATS Cumulative Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_IRATStable_index()
                         })),
                tabPanel("Five-Factor Calendar Method Monthly Abnormal Returns",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderTable({
                           feature_CALtable_index()
                         })),
                tabPanel("Cumulative Abnormal Returns,High, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderDygraph({
                           pnl_plot_interactive(High_feature_Hedged_react_index())
                         })),
                tabPanel("Cumulative Abnormal Returns,Low, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderDygraph({
                           pnl_plot_interactive(Low_feature_Hedged_react_index())
                         })),
                tabPanel("Monthly and Yearly Returns, High, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderUI({
                           renderHeatmapX(pnl_matrix(High_feature_Hedged_react_index()))
                         })),
                tabPanel("Monthly and Yearly Returns, Low, 12m hold",
                         busyIndicator("Calculating results ...",wait = 0),
                         renderUI({
                           renderHeatmapX(pnl_matrix(Low_feature_Hedged_react_index()))
                         }))
    ),style='width: 100%;'))
```
